### 2021-04-28 README.Rmd
V1 Version for submission to Social Science & Medicine

```{r table-food-bank-info, echo=FALSE, results='asis'}
foodbank_table %>% kable("latex",
                         booktabs = TRUE,
                         align = ("cccccc"),
                         col.names = c("Type", 
                                       "Description", 
                                       "Locations Pre-COVID", 
                                       "Locations During COVID", 
                                       "Additional Notes"),
                         caption = "\\label{tab:food-bank-info}foodbank and Food Service Information.",
                         escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(5, width = "15em")
```

@@

```{r table-accessibility-by-age-group, echo=FALSE, results='asis'}
accessibility_by_age %>%
  kable("latex",
        booktabs = TRUE,
        align = ("lcccccc"),
        col.names = c("Accessibility Quartile",
                      "Children (age $\\le$ 18)", 
                      "Adults (19-64)", 
                      "Seniors (age $\\ge$ 65)", 
                      "Children (age $\\le$ 18)", 
                      "Adults (19-64)", 
                      "Seniors (age $\\ge$ 65)"),
        caption = "\\label{tab:accessibility-by-age}Population at each accessibility level by age group among members households with incomes less than CAD40,000.",
        escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>%
  add_header_above(c(" " = 1, "Pre-COVID-19" = 3, "During COVID-19" = 3)) %>%
  footnote(general = c("Population values have been rounded.", 
                       "The values in brackets for population during COVID-19 are the changes from before the pandemic."))
```

@@

In the absence of information regarding how food insecure households travel to food banks and related services, we examined accessibility to food banks using a 15 minutes (one way) travel time threshold. The fact that we must rely on a standard created for accessible drinking water in the developing world only serves to highlight the tragedy of food insecurity in an affluent country like Canada. More broadly, it points to the absurd need to understand how a bad situation was made worse by the pandemic: in effect, the analysis reveals that disparities in accessibility to food banks and services predated the pandemic, that the pandemic contributed to the deterioration of these services, and that populations already in distress, particularly children, ended up in an even more adverse state. How much worse, it is impossible to say, mainly because there is also a dearth of information, let alone standards, regarding what is an _acceptable_ or _sufficient_ level of service when it comes to food banks. Whether this is one facility per 1,000 population or three facilities per 1,000 population, or any other number, we know not.

>>>>

```{r table-food-bank-info, echo=FALSE, results='asis'}
foodbank_table %>% kable("html",
                         booktabs = TRUE,
                         align = ("cccccc"),
                         col.names = c("Type", 
                                       "Description", 
                                       "Locations Pre-COVID", 
                                       "Locations During COVID", 
                                       "Additional Notes"),
                         caption = "\\label{tab:food-bank-info}foodbank and Food Service Information.",
                         escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(5, width = "15em")
```

@@

```{r table-accessibility-by-age-group, echo=FALSE, results='asis'}
accessibility_by_age %>%
  kable("html",
        booktabs = TRUE,
        align = ("lcccccc"),
        col.names = c("Accessibility Quartile",
                      "Children (age <= 18)", 
                      "Adults (19-64)", 
                      "Seniors (age >= 65)", 
                      "Children (age <= 18)", 
                      "Adults (19-64)", 
                      "Seniors (age >= 65)"),
        caption = "\\label{tab:accessibility-by-age}Population at each accessibility level by age group among members households with incomes less than CAD40,000.",
        escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped")) %>%
  add_header_above(c(" " = 1, "Pre-COVID-19" = 3, "During COVID-19" = 3)) %>%
  footnote(general = c("Population values have been rounded.", 
                       "The values in brackets for population during COVID-19 are the changes from before the pandemic."))
```

@@

In the absence of information regarding how food insecure households travel to food banks and related services, we examined accessibility to food banks using a 15 minutes (one-way) travel time threshold. The fact that we must rely on a standard created for accessible drinking water in the developing world only serves to highlight the tragedy of food insecurity in an affluent country like Canada. More broadly, it points to the absurd need to understand how a bad situation was made worse by the pandemic: in effect, the analysis reveals that disparities in accessibility to food banks and services predated the pandemic, that the pandemic contributed to the deterioration of these services, and that populations already in distress, particularly children, ended up in an even more adverse state. How much worse, it is impossible to say, mainly because there is also a dearth of information, let alone standards, regarding what is an _acceptable_ or _sufficient_ level of service when it comes to food banks. Whether this is one facility per 1,000 population or three facilities per 1,000 population, or any other number, we know not. But like international human rights standards for accessibility to clean drinking water within 30 minutes (round-trip), this work strongly suggests that adopting better defined standards for access to food banks that move beyond generalized conceptualizations of "access" to consider the geographic component of accessibility (and its interactions with travel behaviour and individual/household socioeconomic and demographic traits) would make a meaningful contribution to understanding food access and "food bank deserts" for food insecure populations.
